Transparency of COVID-19-related research - Analysis

### 2022-04-01 rmarkdown-covid-19-transparent-analysis.Rmd
The first draft of the results with the figure

---
title: "Transparency of COVID-19-related research - Analysis"
author: Ahmad Sofi-Mahmudi, Eero Raittio
date: "2022-02-11"
output: html_document
---

@@

```{r}
pacman::p_load(tidyverse,
               lubridate, 
               here, 
               ggplot2,
               knitr)
```

```{r, setup, include=FALSE}
# knitr::opts_knit$set(root.dir = '~/Documents/GitHub/covid-transparency/data')
```

@@

# Results
Number of all papers (open access and non open access), open-access papers and open-access percentage:
```{r}
kable(data.frame(hits_all = 175550, 
           hits_oa = nrow(opendata),
           oa_percentage = round((nrow(opendata)/175550)*100, 2)))
```

@@

The number and percentage of papers with a conflict of interest (CoI) disclosure:
```{r}
kable(data.frame(
  number = length(opendata$is_coi_pred[opendata$is_coi_pred == TRUE]),
           percentage = round(length(opendata$is_coi_pred[opendata$is_coi_pred == TRUE])/nrow(opendata)*100, 2)
           ))
```

@@

kable(round(epi.prev(pos = length(opendata$is_coi_pred[opendata$is_coi_pred == TRUE]),
         tested = nrow(opendata),
         se = 0.992,
         sp = 0.995)$ap, 
      2))
```

Comparing CoI disclosure rate in two years:
```{r}
kable(round(prop.table(table(opendata$is_coi_pred, opendata$year_firstpub), 2)*100, 1))
```

@@

The number and percentage of papers with a funding statement:
```{r}
kable(data.frame(number = length(opendata$is_fund_pred[opendata$is_fund_pred == TRUE]),
           percentage = round(length(opendata$is_fund_pred[opendata$is_fund_pred == TRUE])/nrow(opendata)*100, 2)
           ))
```

@@

kable(round(epi.prev(pos = length(opendata$is_fund_pred[opendata$is_fund_pred == TRUE]),
         tested = nrow(opendata),
         se = 0.997,
         sp = 0.981)$ap, 
      2))
```

Comparing funding statement rate in two years:
```{r}
kable(round(prop.table(table(opendata$is_fund_pred, opendata$year_firstpub), 2)*100, 1))
```

@@

The number and percentage of papers that were registered beforehand:
```{r}
kable(data.frame(number = length(opendata$is_register_pred[opendata$is_register_pred == TRUE]),
           percentage = round(length(opendata$is_register_pred[opendata$is_register_pred == TRUE])/nrow(opendata)*100, 2)
           ))
```

@@

kable(round(epi.prev(pos = length(opendata$is_register_pred[opendata$is_register_pred == TRUE]),
         tested = nrow(opendata),
         se = 0.955,
         sp = 0.997)$ap, 
      2))
```

Comparing registration rate in two years:
```{r}
kable(round(prop.table(table(opendata$is_register_pred, opendata$year_firstpub), 2)*100, 1))
```

@@

The number and percentage of papers that shared data:
```{r}
kable(data.frame(number = length(opendata$is_open_data[opendata$is_open_data == TRUE]),
           percentage = round(length(opendata$is_open_data[opendata$is_open_data == TRUE])/nrow(opendata)*100, 2)
           ))
```

@@

kable(round(epi.prev(pos = length(opendata$is_open_data[opendata$is_open_data == TRUE]),
         tested = nrow(opendata),
         se = 0.758,
         sp = 0.986)$ap, 
      2))
```

Comparing data sharing rate in two years:
```{r}
kable(round(prop.table(table(opendata$is_open_data, opendata$year_firstpub), 2)*100, 1))
```

@@

The number and percentage of papers that shared code:
```{r}
kable(data.frame(number = length(opendata$is_open_code[opendata$is_open_code == TRUE]),
           percentage = round(length(opendata$is_open_code[opendata$is_open_code == TRUE])/nrow(opendata)*100, 2)
           ))
```

@@

kable(round(epi.prev(pos = length(opendata$is_open_code[opendata$is_open_code == TRUE]),
         tested = nrow(opendata),
         se = 0.587,
         sp = 0.997)$ap, 
      2))
```

Comparing sharing code rate in two years:
```{r}
kable(round(prop.table(table(opendata$is_open_code, opendata$year_firstpub), 2)*100, 1))
```

@@

Total number of papers published in journals with no JIF:
```{r}
nrow(opendata) - nrow(db_jif)
```

JIF based on COI disclosure:
```{r}
kable(db_jif %>% 
  group_by(is_coi_pred) %>% 
  summarise(Mean = round(mean(X2020.JIF, na.rm = T),3),
            SD = round(sd(X2020.JIF, na.rm = T),4),
            Median = median(X2020.JIF, na.rm = T),
            IQR = IQR(X2020.JIF, na.rm = T)))
```

@@

with(db_jif, shapiro.test(sample(X2020.JIF[is_coi_pred == TRUE], 5000)))
with(db_jif, shapiro.test(X2020.JIF[is_coi_pred == FALSE]))
```

Data is not normal, hence we will use unpaired two-samples Wilcoxon test.
```{r}
wilcox.test(X2020.JIF~is_coi_pred, data = db_jif, exact = FALSE)
```

JIF based on funding disclosure:
```{r}
kable(db_jif %>% 
  group_by(is_fund_pred) %>% 
  summarise(Mean = round(mean(X2020.JIF, na.rm = T), 3),
            SD = round(sd(X2020.JIF, na.rm = T), 4),
            Median = median(X2020.JIF, na.rm = T),
            IQR = IQR(X2020.JIF, na.rm = T)))
```

@@

with(db_jif, shapiro.test(sample(X2020.JIF[is_fund_pred == TRUE], 5000)))
with(db_jif, shapiro.test(X2020.JIF[is_fund_pred == FALSE]))
```

Data is not normal, hence we will use unpaired two-samples Wilcoxon test.
```{r}
wilcox.test(X2020.JIF~is_fund_pred, data = db_jif, exact = FALSE)
```

JIF based on registration:
```{r}
kable(db_jif %>% 
  group_by(is_register_pred) %>% 
  summarise(Mean = round(mean(X2020.JIF, na.rm = T), 3),
            SD = round(sd(X2020.JIF, na.rm = T), 4),
            Median = median(X2020.JIF, na.rm = T),
            IQR = IQR(X2020.JIF, na.rm = T)))
```

@@

with(db_jif, shapiro.test(X2020.JIF[is_register_pred == TRUE]))
with(db_jif, shapiro.test(sample(X2020.JIF[is_register_pred == FALSE], 5000)))
```

Data is not normal, hence we will use unpaired two-samples Wilcoxon test.
```{r}
wilcox.test(X2020.JIF~is_register_pred, data = db_jif, exact = FALSE)
```

JIF based on data sharing:
```{r}
kable(db_jif %>% 
  group_by(is_open_data) %>% 
  summarise(Mean = round(mean(X2020.JIF, na.rm = T), 3),
            SD = round(sd(X2020.JIF, na.rm = T), 4),
            Median = median(X2020.JIF, na.rm = T),
            IQR = IQR(X2020.JIF, na.rm = T)))
```

@@

with(db_jif, shapiro.test(X2020.JIF[is_open_data == TRUE]))
with(db_jif, shapiro.test(sample(X2020.JIF[is_open_data == FALSE], 5000)))
```

Data is not normal, hence we will use unpaired two-samples Wilcoxon test.
```{r}
wilcox.test(X2020.JIF~is_open_data, data = db_jif, exact = FALSE)
```

JIF based on code sharing:
```{r}
kable(db_jif %>% 
  group_by(is_open_code) %>% 
  summarise(Mean = round(mean(X2020.JIF, na.rm = T), 3),
            SD = round(sd(X2020.JIF, na.rm = T), 4),
            Median = median(X2020.JIF, na.rm = T),
            IQR = IQR(X2020.JIF, na.rm = T)))
```

@@

with(db_jif, shapiro.test(X2020.JIF[is_open_code == TRUE]))
with(db_jif, shapiro.test(sample(X2020.JIF[is_open_code == FALSE], 5000)))
```

Data is not normal, hence we will use unpaired two-samples Wilcoxon test.
```{r}
wilcox.test(X2020.JIF~is_open_code, data = db_jif, exact = FALSE)
```

## Monthly trend
Now, drawing monthly trend for each year:
```{r}
summarybyMonth <- opendata %>%
  group_by(month_firstpub, year_firstpub) %>%
  summarise(counts = n(),
            coi_true = sum(is_coi_pred == TRUE),
            fund_true = sum(is_fund_pred == TRUE),
            reg_true = sum(is_register_pred == TRUE),
            data_true = sum(is_open_data == TRUE),
            code_true = sum(is_open_code == TRUE))

coi_summarybyMonth <- opendata %>%
  group_by(month_firstpub, year_firstpub, is_coi_pred) %>%
  summarise(counts = n())

coi_plot <- coi_summarybyMonth %>%
  ggplot(aes(x = month_firstpub, y = counts, fill = is_coi_pred)) + 
  geom_col(position = position_dodge()) +
  facet_grid(. ~ year_firstpub) +
  geom_bar(stat = "identity") +
  scale_x_discrete(name="Month", limits = 1:12, labels = 1:12) +
  theme_minimal() +
  theme(legend.title = element_blank(), 
        plot.title = element_text(hjust = 0.5)) +
  labs(title = "Conflict of Interest disclosure",
       y = "Number of articles") +
        scale_fill_discrete(labels = c("Without", "With"),
                            guide = guide_legend(reverse=TRUE))

fund_summarybyMonth <- opendata %>%
  group_by(month_firstpub, year_firstpub, is_fund_pred) %>%
  summarise(counts = n())

fund_plot <- fund_summarybyMonth %>%
  ggplot(aes(x = month_firstpub, y = counts, fill = is_fund_pred)) + 
  geom_col(position = position_dodge()) +
  facet_grid(. ~ year_firstpub) +
  geom_bar(stat = "identity") +
  scale_x_discrete(name="Month", limits = 1:12, labels = 1:12) +
  theme_minimal() +
  theme(legend.title = element_blank(), 
        plot.title = element_text(hjust = 0.5)) +
  labs(title = "Funding statement",
       y = "Number of articles") +
        scale_fill_discrete(labels = c("Without", "With"),
                            guide = guide_legend(reverse=TRUE))

reg_summarybyMonth <- opendata %>%
  group_by(month_firstpub, year_firstpub, is_register_pred) %>%
  summarise(counts = n())

reg_plot <- reg_summarybyMonth %>%
  ggplot(aes(x = month_firstpub, y = counts, fill = is_register_pred)) + 
  geom_col(position = position_dodge()) +
  facet_grid(. ~ year_firstpub) +
  geom_bar(stat = "identity") +
  scale_x_discrete(name="Month", limits = 1:12, labels = 1:12) +
  theme_minimal() +
  theme(legend.title = element_blank(), 
        plot.title = element_text(hjust = 0.5)) +
  labs(title = "Registration statement",
       y = "Number of articles") +
        scale_fill_discrete(labels = c("Without", "With"),
                            guide = guide_legend(reverse=TRUE))

data_summarybyMonth <- opendata %>%
  group_by(month_firstpub, year_firstpub, is_open_data) %>%
  summarise(counts = n())

data_plot <- data_summarybyMonth %>%
  ggplot(aes(x = month_firstpub, y = counts, fill = is_open_data)) + 
  geom_col(position = position_dodge()) +
  facet_grid(. ~ year_firstpub) +
  geom_bar(stat = "identity") +
  scale_x_discrete(name="Month", limits = 1:12, labels = 1:12) +
  theme_minimal() +
  theme(legend.title = element_blank(), 
        plot.title = element_text(hjust = 0.5)) +
  labs(title = "Data sharing",
       y = "Number of articles") +
        scale_fill_discrete(labels = c("Without", "With"),
                            guide = guide_legend(reverse=TRUE))

code_summarybyMonth <- opendata %>%
  group_by(month_firstpub, year_firstpub, is_open_code) %>%
  summarise(counts = n())

code_plot <- code_summarybyMonth %>%
  ggplot(aes(x = month_firstpub, y = counts, fill = is_open_code)) + 
  geom_col(position = position_dodge()) +
  facet_grid(. ~ year_firstpub) +
  geom_bar(stat = "identity") +
  scale_x_discrete(name="Month", limits = 1:12, labels = 1:12) +
  theme_minimal() +
  theme(legend.title = element_blank(), 
        plot.title = element_text(hjust = 0.5)) +
  labs(title = "Code sharing",
       y = "Number of articles") +
        scale_fill_discrete(labels = c("Without", "With"),
                            guide = guide_legend(reverse=TRUE))

library(ggpubr)

figure <- ggarrange(coi_plot + rremove("xlab") + theme(axis.text.x=element_blank()), 
                    fund_plot + rremove("xlab") + theme(axis.text.x=element_blank(), strip.text.x = element_blank()),
                    reg_plot + theme(strip.text.x = element_blank()),
                    ncol = 1, nrow = 3, vjust = 1, 
                    align = "hv", common.legend = T, legend = "right")

figure <- ggarrange(coi_plot + rremove("xlab") + theme(axis.text.x=element_blank()), 
                    fund_plot + rremove("xlab") + theme(axis.text.x=element_blank(), strip.text.x = element_blank()),
                    reg_plot + rremove("xlab") + theme(axis.text.x=element_blank(), strip.text.x = element_blank()),
                    data_plot + rremove("xlab") + theme(axis.text.x=element_blank(), strip.text.x = element_blank()),
                    code_plot + theme(strip.text.x = element_blank()),
                    ncol = 1, nrow = 5, vjust = 1, 
                    align = "hv", common.legend = T, legend = "right")

# tiff("Figure.tiff", width = 6, height = 11, units = "in", res = 300)
figure
#dev.off()
```

>>>>

---
title: "Transparency of COVID-19-related research - Analysis"
author: Ahmad Sofi-Mahmudi, Eero Raittio, Sergio E. Uribe
date: "2022-02-11"
output: html_document
---

@@

```{r}
pacman::p_load(tidyverse,
               lubridate, 
               here, 
               ggplot2,
               knitr,
               here)
```

@@

# Results
Number of all papers (open access and non open access), open-access papers and open-access percentage:
```{r}
kable(data.frame(hits_all = 175550, 
           hits_oa = 133470,
           oa_percentage = round((133470/175550)*100, 1)))
```

Undownloadable papers:
```{r}
c(number = 133470 - nrow(opendata), 
  percentage = round((133470 - nrow(opendata))/133470*100, 1))
```

@@

The number and percentage of papers with a conflict of interest (CoI) disclosure:
```{r}
kable(data.frame(
  number = length(opendata$is_coi_pred[opendata$is_coi_pred == TRUE]),
           percentage = round(length(opendata$is_coi_pred[opendata$is_coi_pred == TRUE])/nrow(opendata)*100, 1)
           ))
```

@@

kable(round(epi.prev(pos = length(opendata$is_coi_pred[opendata$is_coi_pred == TRUE]),
         tested = nrow(opendata),
         se = 0.992,
         sp = 0.995)$ap, 
      1))
```

Comparing CoI disclosure rate in three years:
```{r}
kable(round(prop.table(table(opendata$is_coi_pred, opendata$year_firstpub), 2)*100, 1))
```

@@

The number and percentage of papers with a funding statement:
```{r}
kable(data.frame(number = length(opendata$is_fund_pred[opendata$is_fund_pred == TRUE]),
           percentage = round(length(opendata$is_fund_pred[opendata$is_fund_pred == TRUE])/nrow(opendata)*100, 1)
           ))
```

@@

kable(round(epi.prev(pos = length(opendata$is_fund_pred[opendata$is_fund_pred == TRUE]),
         tested = nrow(opendata),
         se = 0.997,
         sp = 0.981)$ap, 
      1))
```

Comparing funding statement rate in three years:
```{r}
kable(round(prop.table(table(opendata$is_fund_pred, opendata$year_firstpub), 2)*100, 1))
```

@@

The number and percentage of papers that were registered beforehand:
```{r}
kable(data.frame(number = length(opendata$is_register_pred[opendata$is_register_pred == TRUE]),
           percentage = round(length(opendata$is_register_pred[opendata$is_register_pred == TRUE])/nrow(opendata)*100, 1)
           ))
```

@@

kable(round(epi.prev(pos = length(opendata$is_register_pred[opendata$is_register_pred == TRUE]),
         tested = nrow(opendata),
         se = 0.955,
         sp = 0.997)$ap, 
      1))
```

Comparing registration rate in three years:
```{r}
kable(round(prop.table(table(opendata$is_register_pred, opendata$year_firstpub), 2)*100, 1))
```

@@

The number and percentage of papers that shared data:
```{r}
kable(data.frame(number = length(opendata$is_open_data[opendata$is_open_data == TRUE]),
           percentage = round(length(opendata$is_open_data[opendata$is_open_data == TRUE])/nrow(opendata)*100, 1)
           ))
```

@@

kable(round(epi.prev(pos = length(opendata$is_open_data[opendata$is_open_data == TRUE]),
         tested = nrow(opendata),
         se = 0.758,
         sp = 0.986)$ap, 
      1))
```

Comparing data sharing rate in three years:
```{r}
kable(round(prop.table(table(opendata$is_open_data, opendata$year_firstpub), 2)*100, 1))
```

@@

The number and percentage of papers that shared code:
```{r}
kable(data.frame(number = length(opendata$is_open_code[opendata$is_open_code == TRUE]),
           percentage = round(length(opendata$is_open_code[opendata$is_open_code == TRUE])/nrow(opendata)*100, 1)
           ))
```

@@

kable(round(epi.prev(pos = length(opendata$is_open_code[opendata$is_open_code == TRUE]),
         tested = nrow(opendata),
         se = 0.587,
         sp = 0.997)$ap, 
      1))
```

Comparing sharing code rate in three years:
```{r}
kable(round(prop.table(table(opendata$is_open_code, opendata$year_firstpub), 2)*100, 1))
```

@@

Total number of papers published in journals with a JIF:
```{r}
nrow(db_jif)
```

JIF based on COI disclosure:
```{r}
kable(db_jif %>% 
  group_by(is_coi_pred) %>% 
  summarise(Median = round(median(X2020.JIF, na.rm = T), 1),
            IQR = round(IQR(X2020.JIF, na.rm = T), 2)))

Citation based on COI disclosure:
```{r}
kable(db_jif %>% 
  group_by(is_coi_pred) %>% 
  summarise(Median = round(median(citedByCount, na.rm = T), 1),
            IQR = round(IQR(citedByCount, na.rm = T), 2)))
```

@@

with(db_jif, shapiro.test(sample(X2020.JIF[is_coi_pred == TRUE], 5000)))
with(db_jif, shapiro.test(X2020.JIF[is_coi_pred == FALSE]))

with(db_jif, shapiro.test(sample(citedByCount[is_coi_pred == TRUE], 5000)))
with(db_jif, shapiro.test(citedByCount[is_coi_pred == FALSE]))
```

Data is not normal, hence we will use unpaired two-samples Wilcoxon test.
```{r}
wilcox.test(X2020.JIF~is_coi_pred, data = db_jif, exact = FALSE)

wilcox.test(citedByCount~is_coi_pred, data = db_jif, exact = FALSE)
```

JIF based on funding disclosure:
```{r}
kable(db_jif %>% 
  group_by(is_fund_pred) %>% 
  summarise(Median = round(median(X2020.JIF, na.rm = T), 1),
            IQR = round(IQR(X2020.JIF, na.rm = T), 2)))

Citation based on funding disclosure:
```{r}
kable(db_jif %>% 
  group_by(is_fund_pred) %>% 
  summarise(Median = round(median(citedByCount, na.rm = T), 1),
            IQR = round(IQR(citedByCount, na.rm = T), 2)))
```

@@

with(db_jif, shapiro.test(sample(X2020.JIF[is_fund_pred == TRUE], 5000)))
with(db_jif, shapiro.test(sample(X2020.JIF[is_fund_pred == FALSE], 5000)))

with(db_jif, shapiro.test(sample(citedByCount[is_fund_pred == TRUE], 5000)))
with(db_jif, shapiro.test(sample(citedByCount[is_fund_pred == FALSE], 5000)))
```

Data is not normal, hence we will use unpaired two-samples Wilcoxon test.
```{r}
wilcox.test(X2020.JIF~is_fund_pred, data = db_jif, exact = FALSE)

wilcox.test(citedByCount~is_fund_pred, data = db_jif, exact = FALSE)
```

JIF based on registration:
```{r}
kable(db_jif %>% 
  group_by(is_register_pred) %>% 
  summarise(Median = round(median(X2020.JIF, na.rm = T), 1),
            IQR = round(IQR(X2020.JIF, na.rm = T), 2)))

Citation based on funding disclosure:
```{r}
kable(db_jif %>% 
  group_by(is_register_pred) %>% 
  summarise(Median = round(median(citedByCount, na.rm = T), 1),
            IQR = round(IQR(citedByCount, na.rm = T), 2)))
```

@@

with(db_jif, shapiro.test(X2020.JIF[is_register_pred == TRUE]))
with(db_jif, shapiro.test(sample(X2020.JIF[is_register_pred == FALSE], 5000)))

with(db_jif, shapiro.test(citedByCount[is_register_pred == TRUE]))
with(db_jif, shapiro.test(sample(citedByCount[is_register_pred == FALSE], 5000)))
```

Data is not normal, hence we will use unpaired two-samples Wilcoxon test.
```{r}
wilcox.test(X2020.JIF~is_register_pred, data = db_jif, exact = FALSE)

wilcox.test(citedByCount~is_register_pred, data = db_jif, exact = FALSE)
```

JIF based on data sharing:
```{r}
kable(db_jif %>% 
  group_by(is_open_data) %>% 
  summarise(Median = round(median(X2020.JIF, na.rm = T), 1),
            IQR = round(IQR(X2020.JIF, na.rm = T), 2)))

Citation based on funding disclosure:
```{r}
kable(db_jif %>% 
  group_by(is_open_data) %>% 
  summarise(Median = round(median(citedByCount, na.rm = T), 1),
            IQR = round(IQR(citedByCount, na.rm = T), 2)))
```

@@

with(db_jif, shapiro.test(sample(X2020.JIF[is_open_data == TRUE], 5000)))
with(db_jif, shapiro.test(sample(X2020.JIF[is_open_data == FALSE], 5000)))

with(db_jif, shapiro.test(sample(citedByCount[is_open_data == TRUE], 5000)))
with(db_jif, shapiro.test(sample(citedByCount[is_open_data == FALSE], 5000)))
```

Data is not normal, hence we will use unpaired two-samples Wilcoxon test.
```{r}
wilcox.test(X2020.JIF~is_open_data, data = db_jif, exact = FALSE)

wilcox.test(citedByCount~is_open_data, data = db_jif, exact = FALSE)
```

JIF based on code sharing:
```{r}
kable(db_jif %>% 
  group_by(is_open_code) %>% 
  summarise(Median = round(median(X2020.JIF, na.rm = T), 1),
            IQR = round(IQR(X2020.JIF, na.rm = T), 2)))

Citation based on funding disclosure:
```{r}
kable(db_jif %>% 
  group_by(is_open_code) %>% 
  summarise(Median = round(median(citedByCount, na.rm = T), 1),
            IQR = round(IQR(citedByCount, na.rm = T), 2)))
```

@@

with(db_jif, shapiro.test(X2020.JIF[is_open_code == TRUE]))
with(db_jif, shapiro.test(sample(X2020.JIF[is_open_code == FALSE], 5000)))

with(db_jif, shapiro.test(citedByCount[is_open_code == TRUE]))
with(db_jif, shapiro.test(sample(citedByCount[is_open_code == FALSE], 5000)))
```

Data is not normal, hence we will use unpaired two-samples Wilcoxon test.
```{r}
wilcox.test(X2020.JIF~is_open_code, data = db_jif, exact = FALSE)

wilcox.test(citedByCount~is_open_code, data = db_jif, exact = FALSE)
```

## Sum of five indicators
```{r}
opendata <- opendata %>% mutate(sumOfIndicators = rowSums(opendata %>% select(is_coi_pred, is_register_pred, is_fund_pred, is_open_data, is_open_code)))
```

Number of papers with each number of TRUE indicators:
```{r}
c(five_ind = nrow(filter(opendata, sumOfIndicators == 5)),
  four_ind = nrow(filter(opendata, sumOfIndicators == 4)),
  three_ind = nrow(filter(opendata, sumOfIndicators == 3)),
  two_ind = nrow(filter(opendata, sumOfIndicators == 2)),
  one_ind = nrow(filter(opendata, sumOfIndicators == 1)),
  zero_ind = nrow(filter(opendata, sumOfIndicators == 0)))
```

Percentage of papers with each number of TRUE indicators:
```{r}

c(five_ind = round(nrow(filter(opendata, sumOfIndicators == 5))/nrow(opendata)*100, 1),
  four_ind = round(nrow(filter(opendata, sumOfIndicators == 4))/nrow(opendata)*100, 1),
  three_ind = round(nrow(filter(opendata, sumOfIndicators == 3))/nrow(opendata)*100, 1),
  two_ind = round(nrow(filter(opendata, sumOfIndicators == 2))/nrow(opendata)*100, 1),
  one_ind = round(nrow(filter(opendata, sumOfIndicators == 1))/nrow(opendata)*100, 1),
  zero_ind = round(nrow(filter(opendata, sumOfIndicators == 0))/nrow(opendata)*100, 1))
```

To know which of the indicators were TRUE in papers with two TRUE indicators:
```{r}

nrow_ <- nrow(filter(opendata, sumOfIndicators == 2))

c(coi = round(nrow(filter(opendata, sumOfIndicators == 2 & is_coi_pred))/nrow_*100, 1),
  fund = round(nrow(filter(opendata, sumOfIndicators == 2 & is_fund_pred))/nrow_*100, 1),
  reg = round(nrow(filter(opendata, sumOfIndicators == 2 & is_register_pred))/nrow_*100, 1),
  data = round(nrow(filter(opendata, sumOfIndicators == 2 & is_open_data))/nrow_*100, 1),
  code = round(nrow(filter(opendata, sumOfIndicators == 2 & is_open_code))/nrow_*100, 1))
```

## Monthly trend
Figure 1:
```{r}
library(tibble)

proportions <- opendata %>%
        summarise("COI Disclosure" = sum(is_coi_pred == TRUE),
                  "Funding disclosure" = sum(is_fund_pred == TRUE),
                  "Protocol registration" = sum(is_register_pred == TRUE),
                  "Data sharing" = sum(is_open_data == TRUE),
                  "Code sharing" = sum(is_open_code == TRUE)) %>%
        t() %>%
        as.data.frame() %>%
        rownames_to_column(var = "indicator") %>%
        mutate(percentage = round(V1/nrow(opendata)*100, 1))

p1 <- proportions %>% ggplot() +
        aes(x = reorder(indicator, V1),
            y = V1,
            fill = indicator,
            col = indicator) +
        geom_col(alpha = 0.75) +
        geom_text(aes(label = percentage), hjust = -0.1, size = 3) +
        scale_y_continuous(
                name = "\nNumber of articles (in ten thousands)",
                breaks = seq(0, 10E4, 5E4),
                labels = seq(0, 10, 5),
                expand = expansion(mult = c(0, 0.2))
                ) +
        coord_flip() +
        xlab(NULL) +
        theme(
                legend.position = "none", 
                panel.grid.major.y = element_blank()
        )
```

For the line grapht, first, we add the real publication year and month to the datasets. The real publication year/month is the year/month the paper was first appear online stored in firstPublicationDate column.
```{r}
opendata$YearMonth <- format(as.Date(opendata$firstPublicationDate), "%Y-%m")
```

```{r}
library(ggpubr)

indicator_by_year <- 
        opendata %>% 
        select(YearMonth,
               is_coi_pred,
               is_fund_pred,
               is_register_pred,
               is_open_data,
               is_open_code) %>%
        gather("indicator", "value", -YearMonth) %>%
        count(YearMonth, indicator, value) %>%
        mutate(indicator = recode(indicator,
                                  is_coi_pred = "COI Disclosure",
                                  is_fund_pred = "Funding disclosure",
                                  is_register_pred = "Protocol registration",
                                  is_open_data = "Data sharing",
                                  is_open_code = "Code sharing")) %>%
        complete(indicator, value, YearMonth, fill = list(n = 0)) %>%
        group_by(YearMonth, indicator) %>% 
        mutate(p = n / sum(n)) %>%
        filter(value) %>%
        ungroup()

p2 <-
        indicator_by_year %>% 
        ggplot() +
        aes(x = YearMonth, 
            y = p,
            group = indicator,
            color = indicator) +
        geom_line(size = 0.75) +
        scale_y_continuous(limits = c(0, 1), 
                           labels = scales::percent) +
        scale_color_discrete(name = NULL) +
        scale_fill_discrete(breaks = c("COI Disclosure",
                                       "Funding disclosure",
                                       "Protocol registration",
                                       "Data sharing",
                                       "Code sharing")) +
        labs(y = "Proportion of articles (%)\n", 
             x = "\nMonth") +
        theme(panel.grid.minor = element_blank(),
              legend.position = c(0.2, 0.9),
              axis.text.x = element_text(angle = 45, vjust = 0.9, hjust=1),
              legend.key.size = unit(0.4, 'cm')
              )

figure <- ggarrange(p1, p2,
                    ncol = 2, nrow = 1, 
                    align = "hv", common.legend = F)

# tiff("Figure.tiff", width = 14, height = 7, units = "in", res = 300)
figure
#dev.off()
